The Splashback Radius of Planck-SZ clusters

### 2019-02-14 Paper_v2/RSP_paper_new.tex
small edit

\begin{figure*}
	\centering{
    \includegraphics[scale=0.75]{MAIN_results_with_spline_no_mc.pdf}}
\caption{The main results of the study are presented in this Figure.
The first two rows show the inferred two-dimensional cross-correlation
signals as well as its derivatives.
The three different columns correspond to the three different galaxy
samples cross-correlated with the cluster sample.
The magnitude limit applied to the galaxy catalog is indicated in
each tile of the first row along with the signal-to-noise ratio (SNR).
The measurements of the two-dimensional cross-correlation
signals (black dots) are shown in the first row as well. There, the colored
curves show the two-dimensional model fits of the functional
form in Equation~\ref{eq:surface}. The vertical, shaded regions indicate
the estimates of the locations of steepest slope of the profiles as estimated from the corresponding minima of the two-dimensional
derivative profiles, which are shown in the second row.
Rows three to five show the corresponding three-dimensional model fit
with the functional form Equation~\ref{eq:model} as well as its first and
second order derivatives.
In rows three to five the vertical, shaded regions indicate the
estimates of the splashback radii as estimated from the corresponding minima
of the three-dimensional derivative profiles.
The grey curves show the corresponding, estimated first and second derivatives of the
one-halo term (namely $\rho_{\mathrm{in}}(r)f_{\mathrm{trans}}(r)$ in Equation~\ref{eq:model}).
For comparison, the location of the $r_{\mathrm{200m}}$ radius as calculated
from the average cluster sample properties is indicated by the black, dotted
lines.}
   \label{fig:all_graphs}
\end{figure*}

@@

\textbf{At face value, this result seems to be at odds with the findings
presented by \citet{baxter2017halo}, who find no splashback feature in the blue
galaxy population. Our independent investigations suggest that the splashback
feature gets less prominent as we cross-correlate the galaxy clusters with
galaxies which are progressively bluer in color. In their paper,
\citet{baxter2017halo} considered the last quartile of the blue population.
Therefore, it is conceivable that they see no evidence for the splashback
feature in their dataset in the bluest population of galaxies. We would also
like to note that the approach used by \citet{baxter2017halo} used to separate
galaxies into red and blue populations is also fundamentally different from our
approach. While \citet{baxter2017halo} use K-corrected magnitudes from SDSS
relying on the photometric redshifts of galaxies (which could have different
uncertainties for the red and the blue population), we rely on a color cut
which depends upon the redshift of the cluster under consideration.}

>>>>

\begin{figure*}
	\centering{
    \includegraphics[trim = 0mm 2mm 0mm 0mm, clip, scale=0.8]{MAIN_results_with_spline_no_mc_1.pdf}
    \includegraphics[trim = 0mm 2mm 0mm 0mm, clip, scale=0.8]{MAIN_results_with_spline_no_mc_2.pdf}
}
\caption{The main results of the study are presented in this Figure.
The first two rows show the inferred two-dimensional cross-correlation
signals as well as its derivatives.
The three different columns correspond to the three different galaxy
samples cross-correlated with the cluster sample.
The magnitude limit applied to the galaxy catalog is indicated in
each tile of the first row along with the signal-to-noise ratio (SNR).
The measurements of the two-dimensional cross-correlation
signals (black dots) are shown in the first row as well. There, the colored
curves show the two-dimensional model fits of the functional
form in Equation~\ref{eq:surface}. The vertical, shaded regions indicate
the estimates of the locations of steepest slope of the profiles as estimated from the corresponding minima of the two-dimensional
derivative profiles, which are shown in the second row.
Rows three to five show the corresponding three-dimensional model fit
with the functional form Equation~\ref{eq:model} as well as its first and
second order derivatives.
In rows three to five the vertical, shaded regions indicate the
estimates of the splashback radii as estimated from the corresponding minima
of the three-dimensional derivative profiles.
The grey curves show the corresponding, estimated first and second derivatives of the
one-halo term (namely $\rho_{\mathrm{in}}(r)f_{\mathrm{trans}}(r)$ in Equation~\ref{eq:model}).
For comparison, the location of the $r_{\mathrm{200m}}$ radius as calculated
from the average cluster sample properties is indicated by the black, dotted
lines.}
   \label{fig:all_graphs}
\end{figure*}

@@

\textbf{At face value, this result seems to be at odds with the findings
presented by \citet{baxter2017halo}, who find no splashback feature in the blue
galaxy population. Our independent investigations suggest that the splashback
feature gets less prominent as we cross-correlate the galaxy clusters with
galaxies which are progressively bluer in color. In their paper,
\citet{baxter2017halo} considered the bluest quartile of the galaxy population.
Therefore, it is conceivable that they see no evidence for the splashback
feature in their dataset in the bluest population of galaxies. We would also
like to note that the approach used by \citet{baxter2017halo} used to separate
galaxies into red and blue populations is also fundamentally different from our
approach. While \citet{baxter2017halo} use K-corrected magnitudes from SDSS
relying on the photometric redshifts of galaxies (which could have different
uncertainties for the red and the blue population), we rely on a color cut
which depends upon the redshift of the cluster under consideration.}
